---
title: "Exercise 3"
author: "Linus Rüegg"
date: "5/7/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(readr)        # to import tabular data (e.g. csv)
library(dplyr)        # to manipulate (tabular) data
library(ggplot2)      # to visualize data
library(lubridate)    # To handle dates and times
```


```{r Data Import}
caro <- read_delim("caro60.csv",",")
```
# Task 1


The window v has a size of only 6 minutes.

#### Adding Euclidian Distance
```{r Adding Euclidian Distance}
caro <- caro %>%
  mutate(
    nMinus3 = sqrt((lag(E,2)-E)^2+(lag(N,2)-N)^2),   # distance to pos -3 minutes
    nMinus2 = sqrt((lag(E,2)-E)^2+(lag(N,2)-N)^2),   # distance to pos -2 minutes
    nMinus1 = sqrt((lag(E,1)-E)^2+(lag(N,1)-N)^2),   # distance to pos -1 minutes
    nPlus1  = sqrt((E-lead(E,1))^2+(N-lead(N,1))^2), # distance to pos +1 mintues
    nPlus2  = sqrt((E-lead(E,2))^2+(N-lead(N,2))^2),  # distance to pos +2 minutes
    nPlus3  = sqrt((E-lead(E,2))^2+(N-lead(N,2))^2)  # distance to pos +3 minutes
  )
```



#### Adding mean value per Row
```{r Adding mean value per Row}
caro <- caro %>%
  rowwise() %>%
  mutate(
    stepMean = mean(c(nMinus2, nMinus1,nPlus1,nPlus2))
  ) %>%
  ungroup() 
```

# Task 2

```{r}
ggplot(caro, aes(x= stepMean)) +
  theme_set(theme_minimal()) +
  geom_histogram()
```



```{r}
summary(caro)
```

#### Marking & filtering static values
This is done by calling movements bellow the median of all stepMean (3.6976) static.
I am not quite sure if this is the best way to do this. There might be a better way... (might come back here later)
```{r Marking static values}
caro <- caro %>%
  ungroup() %>%
  mutate(static = stepMean < 3.6976)


caro_filter <- caro %>%
  filter(!static)
```

# Task 3

```{r Plot}
caro%>%
  ggplot(aes(x= E, y= N))  +
  geom_path() +
  geom_point(aes(colour=static)) + 
  coord_equal(1) + 
  labs(color = "Segments") + 
  theme_set(theme_minimal()) +
  theme(legend.position = "bottom")
```

# Task 4
#### Defining Function
```{r Defining Function}
rle_id <- function(vec){
  x <- rle(vec)$lengths
  as.factor(rep(seq_along(x), times=x))
  }
```

#### Applying Function on Caro Data
```{r Applying Function on Caro Data}
caro <- caro %>%
  mutate(segment_id = rle_id(static))
```

#### Plot of the all the segments 
```{r}
caro%>%
  ggplot(aes(x= E, y= N))  +
  geom_path(aes(colour=segment_id)) +
  geom_point(aes(colour=segment_id)) + 
  coord_equal(1) + 
  theme_set(theme_minimal()) +
  theme(legend.position = "none")     
```

#### Removing all Segments shorter than 5
```{r}
caro5plus <- caro %>%
  group_by(segment_id)  %>%
  mutate(n = length(TierID)) %>%
  filter(n >= 5)
```

#### Plot of the segments which presist for more than 5 intervalls
```{r}
caro5plus%>%
  ggplot(aes(x= E, y= N))  +
  geom_path(aes(colour=segment_id)) +
  geom_point(aes(colour=segment_id)) + 
  coord_equal(1) + 
  theme_set(theme_minimal()) +
  theme(legend.position = "none")     
```

# Task 5
```{r Pedestrian Data Import}
pedestrian <- read_delim("pedestrian.csv",",")
```
#### Plotting the Pedestrian Trajectories
```{r Plooting Pedestrian Trajectories}

pedestrian%>%
  ggplot(aes(x= E, y= N))  +
  geom_path(aes(colour=TrajID)) +
  geom_point(aes(colour=TrajID)) + 
  facet_wrap(~TrajID, nrow = 2) +
  coord_equal(1) + 
  theme_set(theme_minimal()) +
  theme(legend.position = "none")     
```

# Task 6

Available functions in the package "SimilarityMeasures"
```{r Similarity Measures}
help(package = "SimilarityMeasures")
library(SimilarityMeasures)
```

Creating matrices of pedestrian coordinates & IDs
```{r Pedestrain Matrix}
pedestrian1 <- as.matrix(filter(pedestrian[,1:3], TrajID == 1))
pedestrian2 <- as.matrix(filter(pedestrian[,1:3], TrajID == 2))
pedestrian3 <- as.matrix(filter(pedestrian[,1:3], TrajID == 3))
pedestrian4 <- as.matrix(filter(pedestrian[,1:3], TrajID == 4))
pedestrian5 <- as.matrix(filter(pedestrian[,1:3], TrajID == 5))
pedestrian6 <- as.matrix(filter(pedestrian[,1:3], TrajID == 6))
```

```{r Creating Distance Matrix}
dtw2 <- DTW(pedestrian1,pedestrian2)
dtw3 <- DTW(pedestrian1,pedestrian3)
dtw4 <- DTW(pedestrian1,pedestrian4)
dtw5 <- DTW(pedestrian1,pedestrian5)
dtw6 <- DTW(pedestrian1,pedestrian6)

dtw <- c(dtw2,dtw3,dtw4,dtw5,dtw6)

ed2 <- EditDist(pedestrian1,pedestrian2)
ed3 <- EditDist(pedestrian1,pedestrian3)
ed4 <- EditDist(pedestrian1,pedestrian4)
ed5 <- EditDist(pedestrian1,pedestrian5)
ed6 <- EditDist(pedestrian1,pedestrian6)

ed <- c(ed2,ed3,ed4,ed5,ed6)

f2 <- Frechet(pedestrian1,pedestrian2)
f3 <- Frechet(pedestrian1,pedestrian3)
f4 <- Frechet(pedestrian1,pedestrian4)
f5 <- Frechet(pedestrian1,pedestrian5)
f6 <- Frechet(pedestrian1,pedestrian6)

fre <- c(f2,f3,f4,f5,f6)

l2 <- LCSS(pedestrian1,pedestrian2)
l3 <- LCSS(pedestrian1,pedestrian3)
l4 <- LCSS(pedestrian1,pedestrian4)
l5 <- LCSS(pedestrian1,pedestrian5)
l6 <- LCSS(pedestrian1,pedestrian6)

lcss <- c(l3,l3,l4,l5,l6)
```
The Frechet distance for trajectory 1 vs 3 could not be found. (to similar?)

LCSS takes super long. Therefore i save the environment in case I need it again.
```{r Save the Environment}
save.image(file='myEnvironment.RData')
```


```{r Tra Names}
tra <- c(2,3,4,5,6)
df_tra <- data.frame(tra, dtw, ed, fre, lcss)
```

```{r Plots}
pdtw <- df_tra%>%
  ggplot(aes(x=tra, y=dtw, fill = tra))  +
  geom_bar(stat="identity", show.legend = FALSE) +
  ggtitle('Distance Time Warping') +
  theme_set(theme_minimal()) 

ped <- df_tra%>%
  ggplot(aes(x=tra, y=ed, fill = tra))  +
  geom_bar(stat="identity", show.legend = FALSE) +
  ggtitle('Edit Distance') +
  theme_set(theme_minimal()) 

pfre <- df_tra%>%
  ggplot(aes(x=tra, y=fre, fill = tra))  +
  geom_bar(stat="identity", show.legend = FALSE) +
  ggtitle('Frechet Distance') +
  theme_set(theme_minimal()) 

plcss <- df_tra%>%
  ggplot(aes(x=tra, y=lcss, fill = tra))  +
  geom_bar(stat="identity", show.legend = FALSE) +
  ggtitle('LCSS') +
  theme_set(theme_minimal()) 
```

```{r Plots in a Grid}
library(patchwork)

grided <- wrap_plots(pdtw, ped, pfre, plcss)
grided + plot_annotation(
  title = 'Comparison of  Similarity Measures',
  subtitle = 'Trajectory 1 compared to the Trajectories 2-6'
)
```



